
% ----------------------------------------------------------------------------------------------------------------------
\section{Related Work {\color{red} Nao mexer por enquanto}}
\label{sec:related}

Recent works explored those areas, to name a few: BigFlow \cite{Viegas2019}
employing Apache Kafka and Apache Flink for distributed stream processing
evaluating with package stream dataset,
CATRACA \cite{Lopez2018,AndreoniLopez2019a} uses 
Apache Kafka and Apache Spark for stream processing and 

\cite{DaCosta2019a}

{\color{red} muito próximo de \cite{Cassales2019a}}
6LoWPAN is a standard defined by the IETF in RFC 6282, to transmit data with
IpV6 and other protocols on low power wireless devices using IEEE 802.15.4 in
the lower layers. However, this technology still lacks protection and security
mechanisms. %\cite{dos-6lowpan-iot, Hybrid-ids-arch-iot, SVELTE}.
%
For instance, in \cite{dos-6lowpan-iot}, signature detection is used to detect
DoS and UDP flood attacks. The architecture uses a probe to promiscuously listen
the whole traffic of a 6LoWPAN network and sends the data to analysis on a
non-constrained host.
%Results were expressed by flood metrics, as the number of packets in the network.
The work in \cite{SVELTE} proposed an hybrid IDS which focuses on specific
routing attacks, such as sink-hole and selective-forwarding. Higher complexity
tasks which demand more computational resources are executed on the border
router, while simpler tasks execute on constrained nodes. Results were expressed
by metrics as recall and memory and energy consumption.
% 
The work in \cite{Hybrid-ids-arch-iot} proposed the use of anomaly detection to
identify internal routing attacks, and signature detection to identify external
attacks. Anomaly detection was tested with simulated attacks, while signature
detection used a subset of NSL-KDD. They used the recall and FAR as metrics.

A three-layer architecture (composed of WSN, Fog and Cloud) with focus on fault
tolerance in disaster scenarios is proposed in \cite{Fault-tolerance-disaster}.
Fog computing is used to execute ML functions and data aggregation. Experiments
used real data collected from sensors. The metrics used included precision,
recall and accuracy.
%
The work in \cite{Kalis} proposed an hybrid IDS which collects information about
the environment and activates specific modules to mitigate each kind of attack.
Experiments were made in a real environment and metrics used were recall,
precision and resource consumption (CPU and RAM).
%
Smart cities scenarios also employ IoT to measuring and monitoring tasks.
%\cite{IoT-arch-smartmeter,scalable-anomaly-detection-smart-city,DS-based-IDS-SmartGrid}.
In \cite{IoT-arch-smartmeter}, the authors propose an architecture that uses
three stream mining methods based on ML to characterize water and energy
consumption behavior, predict consumption, and detect incidents.
The metrics used to express results include water and energy consumption.
%
The work in \cite{scalable-anomaly-detection-smart-city} also aimed to identify
anomalies in a water distribution network and proposes a three layer
architecture (sensors, base stations and datacenter).
The second layer performs time-sensitive tasks, thus reducing latency, while
third layer provides storage and aggregates the results of the second layer with
historical data to generate more accurate information.
Water distribution measures were used, comparing the values of the predictions
with the actual measurements.
%
Intrusion detection for smart cities, based on data mining techniques running on
an unrestricted devices is proposed in \cite{DS-based-IDS-SmartGrid}.
Experiments using KDD99 data are presented and the metrics used were precision,
Kappa, memory consumption, time, FAR, and FNR.


Table \ref{tab:summary} summarizes the discussion on the related work.
Note that some works use data from KDD99 or derived from this dataset.
Collected two decades ago, KDD is no longer representative of current attack
patterns and IoT environments.
Some works used traces captured from local infrastructure, which provide
realistic evaluation, but lack of reproducibility.
Some works used data produced by intentional simulated attacks, designed by the
same people who designed the detection techniques.
This can bring unrealistic advantages to the detection methods.
Also, it is worth noting that most articles used metrics like FAR, recall, and
accuracy.
Although widely adopted in classical scenarios, such metrics are inaccurate for
stream processing \cite{GAMA2010}.

\begin{table*}[htb]
\caption{Summary of related works}
\centering
\begin{scriptsize}
% \begin{tabularx}{\textwidth}{ l m{2cm} | m{2cm} l m{2cm} | m{2cm} | m{2cm} | m{2cm} }
\begin{tabularx}{\textwidth}{l|l|X|X|X}
% \begin{tabularx}{\textwidth}{l|l|X|X|m{3.0cm}}
% Trabalho & Platforma  & Técnica & DataSet & Métricas \\
Work                                         & Platforms    & Technique & DataSet & Metrics\\\hline\hline
% Kasinathan et al
\cite{dos-6lowpan-iot}                       & 6LoWPAN      & Suricata & Real data with metasploit & Accuracy, packets/second\\\hline
% Sheikhan and Bostani
\cite{Hybrid-ids-arch-iot}                   & 6LoWPAN      & Hybrid - MR OPF & NSL-KDD and simulated attacks & FAR and recall\\\hline
% Raza et al
\cite{SVELTE}                                & 6LoWPAN      & DAG analysis & No information & Recall, energy and memory consumption\\\hline
% Furquim et al
\cite{Fault-tolerance-disaster}              & WSN          & MLP of Weka & Real data & MAE, RMSE, R², R, accuracy, recall, precision, specificity\\\hline
% Midi et al
\cite{Kalis}                                 & WSN          & Independent modules, each with one technique & Trace replay and attack injection & Recall, accuracy, memory and CPU consumption\\\hline
% Lloret et al
\cite{IoT-arch-smartmeter}                   & Smart City   & Clustering, MLP and statistical models & Real data from meters & Water and energy consumption\\\hline
% Diffalah et al
\cite{scalable-anomaly-detection-smart-city} & Smart City   & LiSA, smoothing function & Real data & Outliers, comparison between simulation and collected data\\\hline
% Faisal et al
\cite{DS-based-IDS-SmartGrid}                & Smart Grid   & 7 MOA classifiers & KDD99 & Accuracy, Kappa, memory consumption, time, FAR and FNR \\\hline
\end{tabularx}
\label{tab:summary}
\end{scriptsize}
\end{table*}

% ----------------------------------------------------------------------------------------------------------------------
% - Escrever! Corpo:
%   - Proposal (retomar problema {iot, sec, ND}, objetivo, soluções {minas, paralelismo, distribuído, ~~py-kafka, flink,~~ mpi}, propor uma solução)
%   - Implementation (mpi, c, data-structures, data-flow, )
%   - Experiments (rpi, cluster, `evaluate.py`)
%   - Results
%   - Conclusion
% - Demonstrar o paralelismo com figura de pipeline (time vs instruction)
